---
title: "Tidyverse Part II"
author: XXXX
format: html
editor: visual
---

## Instructions

Complete the following exercises using the `lubridate` and `purrr` packages in R. Ensure that your solutions are optimized and use functional programming principles where applicable.

1.  Load the necessary libraries.
2.  Answer each question in separate R code chunks.
3.  Provide detailed explanations for your approach.
4.  Submit the rendered HTML file.

## Functions:

### Question 1

Write a function (using `R` code ) to calculate a z score for a given observed value, a mean, and a standard deviation value. And then use your function to find a z score for the following problem. (Research the internet to find the formula used to calculate a z score)\
Observed value = 25.77, mean = 23.54, standard deviation = 2.442

## List:

### Question 2

```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
```

#### part a.

Why is the vector given above called a list? (Explain in two or three sentences) If the vector is a list, identify the type of each object in the list.

#### part b.

Use and show R code that will give the length of the vector shown above.

#### part c.

Use and show R code that will output the fourth object in the vector shown above.

#### part d.

Use and show R code that will show all objects in the vector (list) given above.

## Advanced Date Manipulation with lubridate

### Question 3:

Generate a sequence of dates from **January 1, 2015** to **December 31, 2025**, spaced by every **two months**. Extract the **year**, **quarter**, and **ISO week number** for each date.

### Question 4:

Given the following dates, compute the difference in **months** and **weeks** between each consecutive pair.

```{r}
sample_dates <- c("2018-03-15", "2020-07-20", "2023-01-10", "2025-09-05")
```

## Higher-Order Functions with purrr

### Question 5:

Using `map()` and `map_dbl()`, compute the **mean**, **median**, and **standard deviation** for each numeric vector in the following list:

```{r}
num_lists <- list(c(4, 16, 25, 36, 49), c(2.3, 5.7, 8.1, 11.4), c(10, 20, 30, 40, 50))
```

## Combining lubridate and purrr

### Question 6:

Given a list of mixed date formats, use `map()` and `possibly()` from `purrr` to safely convert them to **Date** format and extract the **month name**.

```{r}
date_strings <- list("2023-06-10", "2022/12/25", "15-Aug-2021", "InvalidDate")
```

## Submission

-   Save your Quarto file after completing each problem, render it, then stage and commit the changes.\

-   Include well-commented code and clear explanations.\

-   Make at least **one commit per question/part** (atleast 9 meaningfull commits)\

-   Submit the rendered file to **Canvas** and also push it to your **GitHub repository**.\

**Good luck!**
